%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX) XD
%% ---------------------------------------------------------------- 

% Set up the document
\documentclass[a4paper, 11pt, oneside]{Thesis}
\usepackage[utf8]{inputenc}
\usepackage[nonumberlist, seeautonumberlist]{glossaries}
\newglossarystyle{mystyle}{%
  \glossarystyle{long}%
  \renewenvironment{theglossary}%
     {\begin{longtable}{p{3cm}p{\glsdescwidth}}}%
     {\end{longtable}}%
}
\usepackage{hyperref}% http://ctan.org/pkg/hyperref

\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{float}
\usepackage[refpage]{nomencl}
\usepackage{listings}
\usepackage{tabularx,ragged2e,booktabs,caption, makecell}
\usepackage{lipsum}
\usepackage{todonotes}
\usepackage[linesnumbered,algoruled,boxed,lined]{algorithm2e}
\usepackage{eurosym}      %<-- For EURO symbol 
\usepackage{filecontents}
\usepackage{enumitem}
\usepackage{placeins}
\usepackage{multirow}
\usepackage{array}
\usepackage{longtable}
\lstset{escapeinside={<@}{@>}}
\usepackage{subfig} 
\usepackage{float}
\usepackage{graphicx}
\captionsetup{justification=raggedright,
              singlelinecheck=false}
\usepackage[titletoc,toc,page]{appendix}
\usepackage{tikz}
\usetikzlibrary{fadings}
\usepackage{booktabs}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{pdfpages}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[justification=justified,
   format=plain]{caption} % 'format=plain' avoids hanging indentation
\usepackage[%
  backend=biber      % biber or bibtex
 ,style=authoryear    % Alphabeticalsch
 ,style=numeric-comp  % numerical-compressed
 ,sorting=none        % no sorting
 ,sortcites=true      % some other example options ...
 ,block=none
 ,indexing=false
 ,citereset=none
 ,isbn=true
 ,url=true
 ,doi=true            % prints doi
 ,natbib=true         % if you need natbib functions
 ,minnames=8,
 maxnames=10
]{biblatex}
\addbibresource{literature.bib}  
\makeatletter
\def\setChapterprefix#1{\gdef\@Prefix{#1}}
\setChapterprefix{}
\renewcommand*\l@chapter[2]{%
  \ifnum \c@tocdepth >\m@ne
    \addpenalty{-\@highpenalty}%
    \vskip 1.0em \@plus\p@
    \setlength\@tempdima{1.5em}%
    \begingroup
      \parindent \z@ \rightskip \@pnumwidth
      \parfillskip -\@pnumwidth
      \leavevmode \bfseries
      \advance\leftskip\@tempdima
      \hskip -\leftskip
      \@Prefix 
      #1\nobreak\hfil \nobreak\hb@xt@\@pnumwidth{\hss #2}\par
      \penalty\@highpenalty
    \endgroup
  \fi}
    \makeatother


\makeatletter
\renewcommand\fps@figure{!htb}
\setlength\@fptop{0pt} 
\makeatother
\renewcommand{\floatpagefraction}{.6}% before: .5 
\renewcommand{\textfraction}{.15} % before: .2 
\renewcommand{\topfraction}{.8}     % before: .7 
\renewcommand{\bottomfraction}{.5}  % before: .3 
\setcounter{topnumber}{3} % before: 2 
\setcounter{bottomnumber}{1} % before: 1 
\setcounter{totalnumber}{5} % before: 3 

\usepackage{url}

\usepackage{dirtytalk}
\usepackage{notoccite}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{afterpage}
\usepackage{subfig}
\graphicspath{ {images/} }



\lstset{basicstyle=\ttfamily,
	showstringspaces=false,
	commentstyle=\color{red},
	keywordstyle=\color{blue}
}
\lstset{numbers=none}


\newcommand\blankpage{%
	\null
	\thispagestyle{empty}%
	\addtocounter{page}{-1}%
	\newpage}

\SetKwProg{Fn}{Function}{}{}

% Make a glossary and a list of acronyms
\makeglossaries
% Glossary entries
\input{acronyms.tex}
\glsaddall

%------------------------------------------------------------------------------

%% ----------------------------------------------------------------

\begin{document}
\frontmatter      % Begin Roman style (i, ii, iii, iv...) page numbering
% Set up the Title Page
\title{RDF Doctor: A Holistic Approach for Error Detection and Correction of RDF Data}
\authors  {\texorpdfstring
            {{Ahmad Hemid}}
            {Ahmad Hemid}
            }
\addresses  {\groupname \deptname \univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\subject    {}
\keywords   {Access Control}
\maketitle
\blankpage
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round--

% Define the page headers using the FancyHdr package and set up for one-sided printing
  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers

%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here
\Declaration{

% \addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics


I, Ahmed Hemid, declare that this thesis, titled ``RDF Doctor: Holistic RDF Syntax Validation and Error Correction'', and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\end{itemize}

Ahmad Hemid
  
Signature:\\
\rule[1em]{25em}{0.5pt}  % This prints a line for the signature
 
Date:\\
\rule[1em]{25em}{0.5pt}  % This prints a line to write the date
}
\clearpage  % Declaration ended, now start a new page

%--------------------------------------------------------------

%% ----------------------------------------------------------------
% The "Quote Page"
\pagestyle{empty}  % No headers or footers for the following pages

\null\vfill

\textit{``The whole of science is nothing more than a refinement of everyday thinking.``}

\begin{flushright}
	Albert Einstein\\
\end{flushright}

\vfill\vfill\vfill\vfill\vfill\vfill\null
\clearpage  %Quote page ended, start a new page
%% ----------------------------------------------------------------

% The Abstract Page
%\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
	\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
Over the years, the demand for the interoperability support between diverse applications is significantly increased.
Typically, the Resource Definition Framework (RDF) is utilized for the interoperability support and allows for the representation of knowledge and data from various domains.
Moreover, vast amount of data from heterogeneous datasources are continuously published in the RDF format.
Therefore, the RDF documents should be syntactically correct in order to enable software agents for further processing.
Albeit a number of approaches are proposed for ensuring error-free RDF documents, these approaches are commonly not able to identify all syntax errors at the same time by failing on the first encountered error. 
%a number of diverse languages are invented to model and represent data from various domains. 
%The Entity-relationship model, Geographic data model, Generic data model, and lastly the RDF data model are among the most known data modeling languages. 
%The RDF data model is one of the well-known forms of Semantic data model. 
%The main targets of the RDF data model are the processing of meta-data and the exchanging of machine-readable information between web applications. 
%The Subject-Predicate-Object form, known as a triple is used to present information about web resources in the RDF data model. 
%Since the interoperability between applications is the main activity of such model, the correct syntax format used to represent that model is required. 
%Most available tools which check for RDF syntax errors are failed at the first found error. 

In this thesis, we tackle the problem of identifying multiple errors at the same time, and propose RDF-Doctor, a holistic approach for detecting and resolving syntactic errors in an autonomous fashion.
First, we define a comprehensive list of errors that can be detected along with the customized error messages to allow users for better understanding of the actual errors.
Next, special methods are developed to automatically correct syntax errors.
Finally, for a particular number of errors, customized and meaningful messages are delivered to users to facilitate the manual corrections process.
%RDF-Doctor is checking for such errors, listing all of them, and correcting some of them. 
%The solution uses ANTLR parser generator to build the contained parser based on a grammar which injected with error production rules. 
The results from empirical evaluations provide concrete evidences that the presented approach is able to effectively detect a wide range of syntax errors and correct a subset of them.

 

\textit{\small{\textbf{Keywords:} RDF, Error Detection, Error Correction, Syntax Validation}}
%}	
\clearpage  % Abstract ended, start a new page

\acknowledgements{
%	% \addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

This thesis could not have been possible without the help and guidance of some
people. 
Firstly, I would like to thank Prof.Dr. Jens Lehmann and Dr. Steffen Lohmann for letting me pursue my master thesis at the Smart Data Analytics (SDA) group at the Computer Science Department in the University of Bonn.

Next, I would like to thank my thesis advisor Mr. Lavdim Halilaj. 
The door to Mr. Halilaj was always open whenever I had an inquiry about my research or thesis or ran into a problem. He always steered me in the right the direction whenever it is needed.

Special thanks go for Dr. Christoph Lange for being always ready to help with the administrative procedures at Fraunhofer IAIS.
Next, I sincerely thank Prof.Dr. Maria-Esther Vidal. 
I am gratefully indebted to her very valuable comments and advices on this thesis.

Finally, I must express my very profound gratitude to my parents, Mahdia and Madhat; my wife, Tayymaa and my children Abedelrahman, Madhat and Omer for providing me with unfailing support and continuous encouragement throughout my years of study and through the process of researching and writing this thesis. 
This accomplishment would not have been possible without them. 

\hfill
Ahmad
}

% \clearpage  % End of the Acknowledgements
\afterpage{\blankpage}
%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back

%% ----------------------------------------------------------------

\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
%\lhead{\emph{List of Figures}}  % Set the left side page header to "List of Figures"
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
%\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
\listoftables  % Write out the List of Tables

\printglossary[style=mystyle, title=Abbreviations]
%\printglossary[style=mystyle, title=Abbreviations, sort=standard]

%% ----------------------------------------------------------------
%\lhead{\emph{List of Listings}}  % Set the left side page header to "List of Listings"
%\lstlistoflistings  % Write out the List of Listings

%% ----------------------------------------------------------------
\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering



 %% ----------------------------------------------------------------


%% ----------------------------------------------------------------

%\input{chapters/introduction}
%\input{chapters/background}
%\input{chapters/related-work}
%%\input{chapters/motivating-example}
%\input{chapters/datamodel_approach}
%\input{chapters/implementation}
%\input{chapters/experimental-study}
%\input{chapters/conclustion-and-future-work}
%\input{chapters/appendices}
\input{chapters/1_introduction}
\input{chapters/3_preliminaries}
\input{chapters/2_related_work}
\input{chapters/5_approach}
\input{chapters/6_implementation}
\input{chapters/7_evaluation}
\input{chapters/8_conclusions}

%% ----------------------------------------------------------------
\clearpage
%------------------------------------------------------------------------------

\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
\label{Bibliography}
\printbibliography

%\bibliographystyle{unsrtnat}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography\bibliographystyle{plain}
%\nocite{*}
%\bibliography{literature}  % The references (bibliography) information are stored in the file named "Bibliography.bib"
\input{chapters/appendix.tex}

\end{document}  % The End
%% ----------------------------------------------------------------